Gesture Typing on Virtual Tabletop: Effect of Input Dimension on Performance

### 2017-08-22 paper.tex
add dimension to title

\title{Gesture Typing on Virtual Tabletop: Effect of Input on Performance}

@@

% Paper metadata (use plain text, for PDF inclusion and later re-using, if desired)
\def\plaintitle{Gesture Typing on Virtual Surfaces: Effect of Input on Performance}
\def\plainauthor{Name}
\def\plainkeywords{Gesture Input, Gesture Keyboard, Mobile, Continuous Interaction, Tabletop, Text Input}
\def\plaingeneralterms{Documentation, Standardization}

>>>>

\title{Gesture Typing on Virtual Tabletop: Effect of Input Dimension on Performance}

@@

% Paper metadata (use plain text, for PDF inclusion and later re-using, if desired)
\def\plaintitle{Gesture Typing on Virtual Surfaces: Effect of Input Dimension on Performance}
\def\plainauthor{Name}
\def\plainkeywords{Gesture Input, Gesture Keyboard, Mobile, Continuous Interaction, Tabletop, Text Input}
\def\plaingeneralterms{Documentation, Standardization}
